Lake Photic Zone Temperature accross the Conterminous United States

### 2019-07-31 manuscript/manuscript.Rmd
updated figure caption for varsel fig and fixed R cite in .bib

```{r setup, include=FALSE, eval=FALSE}
# source(here::here("R/functions.R"), encoding = "UTF-8")
library(captioner)
#opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)

```

@@

##Random Forest Modelling

@@

Using the average temperature for the upper two meters as the response variable, we initially began the variable selection process with 16 predictor variables.   The variable selection process identified a reduced model with 7 variables (Fig 2). The selected variables were the average ambient air temperature for the sample date, sample date, longitude, average ambient air temperature for 30 day proceeding the sample date, elevation, latitude, length of lake shoreline, and the lake surface area.

![`r fig_num("varsel_fig",caption="Variable selection plot for all variables. Shows percent increase in mean‐squared error as a function of the number of variables.")`](../figures/varselfig.jpg)

>>>>

```{r setup, include=FALSE, eval=TRUE}
# source(here::here("R/functions.R"), encoding = "UTF-8")
library(captioner)
#opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)
```

@@

## Random Forest Modelling

@@

Using the average temperature for the upper two meters as the response variable, we initially began the variable selection process with 16 predictor variables.   The variable selection process identified a reduced model with 7 variables (`r fig_num("varsel_fig",caption="Variable selection plot for all variables. Shows percent increase in mean‐squared error as a function of the number of variables.", display = "cite")`). The selected variables were the average ambient air temperature for the sample date, sample date, longitude, average ambient air temperature for 30 day proceeding the sample date, elevation, latitude, length of lake shoreline, and the lake surface area.

![`r fig_num("varsel_fig")`](../figures/valselfig.jpg)
